Prefetching SPARQL query cacher

### 2016-06-05 dissertation/cache-proxy.tex
add todo
improve transition
proofreading

\begin{table}
\caption{The modules that enable the query cache}\label{tab:modules}
\begin{tabular}{ | l | p{3cm} | l |}
  \hline
  Module & Authors & Github URL \\ \hline

@@

To further understand the roles of the different modules, note the
following: \pmodule{LWP::UserAgent::CHICaching} is a traits-based
\cite{traits} implementation of the majority of RFC7234.
The underlying caching framework used by this module, \pmodule{CHI},
will take care of expiry and purging of entries, since this module
will supply an explicit freshness lifetime. 
\pmodule{AtteanX::Endpoint} is an implementation of the server side of
SPARQL 1.1 Protocol.

@@

Traits are groups of methods that serve as a primitive unit of code
reuse. Traits are not constructed to objects themselves and do not
use inheritance for composition, instead a class is composed by a set of
traits and possibly the class' own methods, and then instantiated. A
trait can also require a set of methods, and as such, is similar to
interfaces, but since its focus is code reuse, it can also provide a
default implementation.

@@

Based on the algebra tree and plans generated by the models or the
default query planner, as well as the access plans, several
alternative plans will be generated, and their cost will be
estimated. How this happens in detail depends on how the planner is
composed. Attean comes with two roles that implement different
planners, \pmodule{Attean::API::SimpleCostPlanner} will compute all
possible plans and then estimate the cost of all plans, and finally
return the best 5. \pmodule{Attean::API::IDPJoinPlanner}, which
implements an Iterative Dynamic Programming planner
\cite{Kossmann:2000:IDP:352958.352982}, which prunes plans
aggressively based on their estimated cost in each iteration of query
plan generation. When a final plan tree has been found, the query may
be executed.

>>>>

\begin{table}
\caption{The modules that enable the query cache\todo{make it fit. Rotate?}}\label{tab:modules}
\begin{tabular}{ | l | p{3cm} | l |}
  \hline
  Module & Authors & Github URL \\ \hline

@@

To further understand the roles of the different modules, note the
following: \pmodule{LWP::UserAgent::CHICaching} is a traits-based
\cite{traits} implementation of the majority of RFC7234.
The underlying caching framework used by this module, \pmodule{CHI},
will take care of expiry and purging of entries, since this module
will supply an explicit freshness lifetime. 
\pmodule{AtteanX::Endpoint} is an implementation of the server side of
SPARQL 1.1 Protocol. The system is further detailed in the following sections:

@@

Traits are groups of methods that serve as a primitive unit of code
reuse. Traits are not constructed to objects themselves and do not
use inheritance for composition, instead a class is composed by a set of
traits and possibly the class' own methods, and then instantiated. A
trait can also require a set of methods or attributes, and as such, is similar to
interfaces, but since its focus is code reuse, it can also provide a
default implementation.

@@

Based on the algebra tree and plans generated by the models or the
default query planner, as well as the access plans, several
alternative plans will be generated, and their cost will be
estimated. How this happens in detail depends on how the planner is
composed. Attean comes with two roles that implement different
planners, \pmodule{Attean::API::SimpleCostPlanner} will compute all
possible plans and then estimate the cost of all plans, and finally
return the best 5. \pmodule{Attean::API::IDPJoinPlanner}
implements an Iterative Dynamic Programming planner
\cite{Kossmann:2000:IDP:352958.352982}, which prunes plans
aggressively based on their estimated cost in each iteration of query
plan generation. When a final plan tree has been found, the query may
be executed.
